\normalsize \headingfont \textbf{Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online} \vspace{-1.5em}

### 2024-04-29 ms/main.tex
Updates from Overleaf

We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}. Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that people in politically conservative states search for pornography and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}. Combining individual-level data on partisanship with direct passive individual level measures of pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa. Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats. Adjusting for background attributes such as age, gender, race, and education, however, make the partisan differences go away. Our findings relate to \cite{Perry2018-cn}, which finds that more religious people are more likely to think of pornography as morally wrong while still consuming pornography.

@@

To code pornographic content, we start by assuming all content marked ``Adult'' as pornographic. This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment'' (e.g., hentainfox.com). YouGov classifies some domains that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org, as Adult. Given the skew in the data (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites. We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica. Domains without a YouGov category are assumed to be non-pornographic sites. In \hyperref[sm:smD]{Appendix D}, we test whether replacing this assumption with the more usual missing-completely-at-random assumption changes the key substantive conclusions. It doesn't.

@@

In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult} in \hyperref[sm:smA]{Appendix A}). As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites. Each of the top 5 non-pornographic sites were visited more than 200,000 times by our panelists. In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.

@@

\begin{figure}[!ht]
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_adultsites_fullsample.pdf}
         \caption{Online pornography}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_nonadultsites_fullsample.pdf}
         \caption{Other online content}
     \end{subfigure}
\caption{Hours Spent on Online Pornography and All Other Online Content}
\label{fig:distribution_duration_on_adultsites_fullsample}
\caption*{\footnotesize \emph{Notes:} 
    Each panel shows the average number of hours spent consuming respective kind of content during the observation period per decile.
    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
    %textbf{FIG??} shows the same figures but only for consumers of pornography.
}
\end{figure}

@@

\subsection{Substitution?}
Are people substituting pornography for other kinds of leisure content? To shed light on that, we examine the relationship between the time spent on online pornography and time spent on other leisure-related online sites. We fit a locally weighted linear regression after removing extreme values (90th percentile) (for visualization or else the graph is dominated by the tail on which we have the least data) in online consumption. We see no evidence of substitution.

@@

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in Hours Spent on Pornography}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
            Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
        \cref{tab:quantile-estimates-hours} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
	\caption*{\footnotesize \emph{Notes:} 
	The dependent variable is the percentage of time individuals in our sample spent on pornographic sites. Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis. Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
            \cref{tab:quantile-estimates-time} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

Looking at differences in the percentage of partisans who consume any pornographic content, we find little difference as well. Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).

@@

%=====================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (with covariates) 
%=====================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot without covariates.
  \cref{tab:quantile-estimates-hours} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration_covariates}
\end{figure}

%================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (with covariates) 
%================================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		Covariates included: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
        \cref{tab:quantile-estimates-time} in \hyperref[sm:smB]{Appendix B} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration_covariates}
\end{figure}

Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). 
%Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). 
How do differences in age and other such demographic differences between the parties ``explain'' the results? To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}. As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away. 
%(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.) 
%Using alternative classifications of pornography sites led to similar conclusions (\cref{sec:robustness}).

\subsection{Robustness}\label{sec:robustness}
We replicate our analyses using four alternative classifications of domains and obtain similar results (see \hyperref[sm:smE]{Appendix E}).  
In \hyperref[sm:smG]{Appendix G}, we also analyze similar metrics for the total number of visits and proportion of visits instead of time. 
The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}). 
\hyperref[sm:smH]{Appendix H} replicates key findings by dropping domains with missing YouGov domain category.

@@

The second concern is that our measures are a point in time. We have data from one month in one year - June 2022. It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.

@@

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}[h]
	\centering
	\caption{Top 25 Non-Pornographic Sites}
	\includegraphics[width=\textwidth]{figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows the top 25 non-pornographic sites visited by the sample.
		The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
		The \emph{Visits} column is the total number of visits by individuals in the sample to the site.  			
		Sites to the right of the vertical dashed are the top 1 percent of non-pornographic sites in visits.
	}
	\label{fig:top25_nonadult}
\end{figure}

%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows the top 25 pornographic sites that individuals visited in the sample period.
		Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
    	The \emph{Hours} column is the total number of hours individuals in the sample spent on the site. 
    	The \emph{Visits} column is the total number of visits by individuals in the sample to the site.
            Sites to the right of the vertical dashed are the top 1 percent of pornographic sites in visits.
	}
	\label{fig:top25_adult}
\end{figure}

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\includegraphics[width=.5\textwidth]{figs/concentration_porn_consumption.pdf}
	\caption{Top 10 Pornographic Sites vs. Other Pornographic Sites}
	\caption*{\footnotesize \emph{Notes:} 
            The average minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
            The top 10 pornographic sites are determined by the total amount of time spent on each site by all individuals over the sample period.
            Data is at the individual-domain level (n = 2.4k).
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

@@

\FloatBarrier
\subsubsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online Among People Who Consumed Any Pornography}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

@@

\begin{figure}[!h]
\label{fig:tu_prop_entertainment-prop_pure_adult}
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
         \caption{Entertainment}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
         \caption{Shopping}
     \end{subfigure}
\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
\caption*{\footnotesize \emph{Notes:}
Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs time spent on other non-adult leisure (``entertainment'' and ``shopping'').
Observations above the 90th percentile are omitted. 
Non-adult entertainment sites are those with YouGov categories containing ``entertainment'' (e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.)---top five of such sites are youtube.com, hideout.co, hulu.com, netflix.com, and yahoo.com.
Non-adult shopping sites are those with YouGov categories containing ``shopping'' (e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.)---top five of such sites are amazon.com, ebay.com, walmart.com, etsy.com, capitaloneshopping.com, and craigslist.org.
Top five pure adult sites are: xvideos.com, pornhub.com, xnxx.com, rule34.xxx, and xhamster.com (see \cref{fig:top25_adult}).
Each estimation in the Lowess uses .3 of the sample data.
The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
}
\end{figure}

@@

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates_mar} for the same plot controlling for individual characteristics.
            \cref{fig:quantile_regression_prop_duration} in main body.
	}
	\label{fig:quantile_regression_prop_duration_mar}
\end{figure}

%================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (with covariates) 
%================================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		Covariates included on the right-hand side are: gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_mar} for the same plot without covariates.
            \cref{fig:quantile_regression_prop_duration_covariates} in main body.
	}
	\label{fig:quantile_regression_prop_duration_covariates_mar}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=.6\linewidth]{figs/forcepoint_quantile_reg_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (Forcepoint ThreatSeeker)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:forcepoint_quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:forcepoint_quantile_regression_duration}
\end{figure}

>>>>

We also use the data to contribute to the small literature connecting political conservatism to opposition to pornography \citep{Peek1982-ua, Woodrum1992-vk}. Despite the expected relationships between religiosity, political conservatism, and opposition to pornography \citep{Wright2013-an, Perry2018-cn}, recent research using aggregate data has shown that people in politically conservative states search for pornography and subscribe to online adult services more often \citep{macinnis2015american, edelman2009markets}. Combining individual-level data on partisanship with direct passive individual-level measures of pornography consumption, we shed light on whether Democrats consume more pornography than Republicans or vice versa. Superficially, our browsing data suggest Republicans in the right tail of the distribution consume more online pornography than Democrats. Adjusting for background attributes such as age, gender, race, and education, however, makes the partisan differences go away. Our findings relate to \cite{Perry2018-cn}, which finds that more religious people are more likely to think of pornography as morally wrong while still consuming pornography.

@@

To code pornographic content, we start by assuming all content marked ``Adult'' as pornographic. This includes ``Adult, Business'' (e.g., onlyfans.com) and ``Adult, Entertainment,'' e.g., \texttt{hentainfox.com}. YouGov classifies some domains that do not primarily carry pornographic content, e.g., \texttt{urbandictionary.com} and \texttt{4chan.org}, as Adult. Given the skew in the data (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult}), we manually checked the top few hundred adult domains (constituting well over 99\% of the adult content consumed) to remove such sites. We code a domain as carrying pornographic content if there is nudity on the landing page or if the site is some form of erotica. Domains without a YouGov category are assumed to be non-pornographic sites. In \hyperref[sm:smD]{Appendix D}, we test whether replacing this assumption with the more usual missing-completely-at-random assumption changes the key substantive conclusions. It doesn't.

@@

In line with previous research \citep{hindman2009myth, Dewan2004-tt}, we find a considerable skew in online media consumption (see \cref{fig:top25_nonadult} and \cref{fig:top25_adult} in \hyperref[sm:smA]{Appendix A}). As \cref{fig:top25_nonadult} shows, the big tech and social media companies occupy most of the top 25 most frequently visited websites. Each of the top 5 non-pornographic sites was visited more than 200,000 times by our panelists. In comparison, the 99th percentile non-pornographic site was visited only 1,652 times by our panelists during the observation period.

@@

\begin{figure}[!ht]
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_adultsites_fullsample.pdf}
         \caption{Online pornography}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/distribution_duration_on_nonadultsites_fullsample.pdf}
         \caption{Other online content}
     \end{subfigure}
\caption{Hours Spent on Online Pornography and All Other Online Content}
\label{fig:distribution_duration_on_adultsites_fullsample}
\caption*{\footnotesize \emph{Notes:} 
    Each panel shows the average number of hours spent consuming the respective kind of content during the observation period per decile.
    Individuals (n = 1135) are split into deciles, with each bin containing approximately the same number of individuals.
    Capped vertical bars are bootstrapped 95\% confidence intervals (n = 10,000).
    %textbf{FIG??} shows the same figures but only for consumers of pornography.
}
\end{figure}

@@

\subsection{Substitution?}
Are people substituting pornography for other kinds of leisure content? To shed light on that, we examine the relationship between the time spent on online pornography and time spent on other leisure-related online sites. We fit a locally weighted linear regression after removing extreme values (90th percentile) (for visualization, or else the graph is dominated by the tail on which we have the least data) in online consumption. We see no evidence of substitution.

@@

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in Hours Spent on Pornography}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
            Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
        \cref{tab:quantile-estimates-hours} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
	\caption*{\footnotesize \emph{Notes:} 
	The dependent variable is the percentage of time spent on pornographic sites. Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis. Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates} for the same plot controlling for individual characteristics.
            \cref{tab:quantile-estimates-time} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration}
\end{figure}

@@

Differences in the percentage of partisans who consume any pornographic content reveal little difference as well. Nearly 31\% percent of Democrats and 30\% percent of Republicans consumed at least some pornography online in June 2022; the difference between the two is not statistically significant (\cref{fig:consume_porn_yes_no}).

@@

%=====================================================
% Fig of quantile regression estimates
% Time Spent on Adult Sites by Party (with covariates) 
%=====================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		Covariates included on the right-hand side are gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration} for the same plot without covariates. \cref{tab:quantile-estimates-hours} tabulates the estimates.
	}
	\label{fig:quantile_regression_duration_covariates}
\end{figure}

%================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (with covariates) 
%================================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/quantile_reg_covariates_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration} for the same plot without covariates.
        \cref{tab:quantile-estimates-time} tabulates the estimates.
	}
	\label{fig:quantile_regression_prop_duration_covariates}
\end{figure}

Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). How do differences in age and other such demographic differences between the parties ``explain'' the results? To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}. As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away. 
%(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.) 
%Using alternative classifications of pornography sites led to similar conclusions (\cref{sec:robustness}).

\subsection{Robustness}\label{sec:robustness}
\hyperref[sm:smD]{Appendix D} replicates key findings by dropping domains with missing YouGov domain categories. We also replicate our analyses using four alternative classifications of domains and obtain similar results (see \hyperref[sm:smE]{Appendix E}). In \hyperref[sm:smF]{Appendix F}, we analyze the impact on the total number of visits and the percentage of visits instead of time. The upshot is that the key conclusions are unaffected (see \cref{tab:distribution_visits_party} and \cref{tab:distribution_prop_visits_party}).

@@

The second concern is that our measures are a point in time. We have data from one month in one year---June 2022. It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in the preceding or following months.

@@

%================================
% Figure of top 25 non-adultsites
%================================
\begin{figure}[h]
	\centering
	\caption{Top 25 Non-Pornographic Sites}
	\includegraphics[width=\textwidth]{figs/top_25_nonadultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows the top 25 non-pornographic sites visited by respondents in the sample period.
		The \emph{Hours} column is the total number of hours spent by all the respondents in the sample period.
    	The \emph{Visits} column is the total number of visits by all the respondents in the sample period.			
		Sites to the right of the vertical dashed are the top 1 percent of non-pornographic sites in visits.
	}
	\label{fig:top25_nonadult}
\end{figure}

%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows the top 25 pornographic sites visited by respondents in the sample period. Pornography sites are categorized by YouGov (see the \nameref{sec:data} section).
    	The \emph{Hours} column is the total number of hours spent by all the respondents in the sample period.
    	The \emph{Visits} column is the total number of visits by all the respondents in the sample period.
            Sites to the right of the vertical dashed are the top 1 percent of pornographic sites in visits.
	}
	\label{fig:top25_adult}
\end{figure}

%=============================================
% Figure for concentration of porn consumption
%=============================================
\begin{figure}
	\centering
	\includegraphics[width=.5\textwidth]{figs/concentration_porn_consumption.pdf}
	\caption{Top 10 Pornographic Sites vs. Other Pornographic Sites}
	\caption*{\footnotesize \emph{Notes:} 
            The average number of minutes spent on the top 10 pornographic sites vs. all other pornographic sites.
            The top 10 pornographic sites are determined by the total amount of time spent on each site by all the respondents during the sample period.
            Data is at the individual-domain level (n = 2.4k).
		Vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption}
\end{figure}

@@

\FloatBarrier
\subsubsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online Among People Who Consumed Any Pornography}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the number of hours spent by individuals who consumed pornography in the sample period. 
		See \cref{tab:distribution_prop_duration} for the distribution in terms of percentage of time.
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

@@

\begin{figure}[!h]
\label{fig:tu_prop_entertainment-prop_pure_adult}
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_entertainment-duration_pure_adult.pdf}
         \caption{Entertainment}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_shop-duration_pure_adult.pdf}
         \caption{Shopping}
     \end{subfigure}
\caption{Time Spent on Online Pure Pornography vs. Non-adult Leisure}
\caption*{\footnotesize \emph{Notes:}
Lowess for time spent on online pornography (as defined in \nameref{subsec:measuring_porn_content}) vs. time spent on other non-adult leisure (``entertainment'' and ``shopping'') with a bandwidth of .3.
Observations above the 90th percentile are omitted. Non-adult entertainment sites are those with YouGov categories containing ``entertainment,'' e.g., ``Entertainment, Streaming Media'', ``Education, Entertainment, Streaming Media'', ``Business, Entertainment'', etc.---top five such sites are \texttt{youtube.com}, \texttt{hideout.co}, \texttt{hulu.com}, \texttt{netflix.com}, and \texttt{yahoo.com}. Non-adult shopping sites are those with YouGov categories containing ``shopping,'' e.g., ``Shopping'', ``Business, Shopping'', ``Messageboards and Forums, Shopping'', etc.---top five of such sites are \texttt{amazon.com}, \texttt{ebay.com}, \texttt{walmart.com}, \texttt{etsy.com}, \texttt{capitaloneshopping.com}, and \texttt{craigslist.org}.
Top five pure adult sites are: \texttt{xvideos.com}, \texttt{pornhub.com}, \texttt{xnxx.com}, \texttt{rule34.xxx}, and \texttt{xhamster.com} (see \cref{fig:top25_adult}).
The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).
Swapping the horizontal axis for any adult content looks similar in \cref{fig:tu_prop_entertainment-prop_adult_duration}. 
}
\end{figure}

@@

%========================================
% Quantile regressions
% Proportion of time spent on adult sites
%========================================
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time a person spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_covariates_mar} for the same plot controlling for individual characteristics.
            \cref{fig:quantile_regression_prop_duration} in main body.
	}
	\label{fig:quantile_regression_prop_duration_mar}
\end{figure}

%================================================================
% Fig of quantile regression estimates
% Percentage Time Spent on Adult Sites by Party (with covariates) 
%================================================================
\begin{figure}[!ht]
	\centering
	\includegraphics[width=.7\linewidth]{figs/mar/quantile_reg_covariates_proportion_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in the Percentage of Time Spent on Pornography (with covariates)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the percentage of time a person spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		The covariates included gender (Female/Male), race (White/Black/Hispanic/Asian/Others), education level (no HS/HS graduate/some college/college graduate), age and its quadratic, and region (NE/MW/S/W).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_prop_duration_mar} for the same plot without covariates.
            \cref{fig:quantile_regression_prop_duration_covariates} in main body.
	}
	\label{fig:quantile_regression_prop_duration_covariates_mar}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=.6\linewidth]{figs/forcepoint_quantile_reg_duration_adult.pdf}
	\caption{Distribution of Partisan Differences in Hours Spent on Pornography (Forcepoint ThreatSeeker)}
	\caption*{\footnotesize \emph{Notes:} 
		The dependent variable is the number of hours a person spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
  Figure shows 19 quantile estimates (5th--95th percentile in steps of 5).
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:forcepoint_quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:forcepoint_quantile_regression_duration}
\end{figure}
